### 2025-02-04 Paper/computers&geosiciences/CAGEO_LaTeXTemplate-main/manuscript.tex
adfa

\begin{abstract}
Rockfall events are a type of natural disaster that causes loss of life and property in the world. The risk of rockfall can be eliminated by using rockfall prevention methods. To choose the most suitable method, projecting studies should be carried out. This study aims to automatically detect rock blocks in a region and calculate their volumes and 3D surface areas. For this purpose, U-Net segmentation method and Python software language were used. DenseNet121 transfer learning method based on convolutional neural networks was used for feature extraction. The data set was created from the orthophoto images obtained by an unmanned aerial vehicle (UAV). Using the random sampling method, 369 images were selected for training and 191 images for test. As a result of the analysis, the mean IOU (Intersection Over Union) was calculated as 85\% for training and 84\% for test. The trained model was applied to the study area and 3111 rock blocks were detected. The resulting map is saved as a vector file with coordinates and can be opened in any GIS software. The volumes and 3D surface areas of the rock blocks were calculated with Python software as 275.93 m$^3$ and 2615.23 m$^2$, respectively. With this study, rock blocks can be detected automatically, and their volumes and 3D surface areas can be measured. These results can be used in the selection of rockfall prevention methods. In addition, the codes used in this study can automatically detect different geological formations from aerial photographs. Also, volume and 3D surface area algorithms developed in this study can be used to calculate different types of objects.
\end{abstract}

@@

\begin{equation}
\label{eqn:eq2}
F1\text{-}Score = \frac{2 \times \text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}}
\end{equation}
\[
\text{Precision} = \frac{TP}{TP + FP}
\]
\[
\text{Recall} = \frac{TP}{TP + FN}
\]
Where TP is True Positive, FP is False Positive and FN is False Negative.

@@

The 3D surface area is calculated as following:
\begin{equation}
\label{eqn:eq7}
\text{3D surface area} = \text{pixel area} \times \text{slope correction}
\end{equation}

>>>>

\begin{abstract}
Rockfall events are a type of natural disaster that causes loss of life and property in the world. The risk of rockfall can be eliminated by using rockfall prevention methods. To choose the most suitable method, projecting studies should be carried out. This study aims to automatically detect rock blocks in a region and calculate their volumes and 3D surface areas. For this purpose, U-Net segmentation method and Python software language were used. DenseNet121 transfer learning method based on convolutional neural networks was used for feature extraction. The data set was created from the orthophoto images obtained by an unmanned aerial vehicle (UAV). Using the random sampling method, 369 images were selected for training and 191 images for test. As a result of the analysis, the IOU (Intersection Over Union) was calculated as 85\% for training and 84\% for test. The trained model was applied to the study area and 3111 rock blocks were detected. The resulting map is saved as a vector file with coordinates and can be opened in any GIS software. The volumes and 3D surface areas of the rock blocks were calculated with Python script as 275.93 m$^3$ and 2615.23 m$^2$, respectively. With this study, rock blocks can be detected automatically, and their volumes and 3D surface areas can be measured. These results can be used in the selection of rockfall prevention methods. In addition, the codes used in this study can automatically detect different geological formations from aerial photographs. Also, volume and 3D surface area algorithms developed in this study can be used to calculate different types of objects.
\end{abstract}

@@

\begin{equation}
\label{eqn:eq2}
F1\text{-}Score = \frac{2 \times \text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}}
\end{equation}

\begin{equation}
\label{eqn:eq3}
\text{Precision} = \frac{TP}{TP + FP}
\end{equation}

\begin{equation}
\label{eqn:eq4}
\text{Recall} = \frac{TP}{TP + FN}
\end{equation}
Where TP is True Positive, FP is False Positive and FN is False Negative.

@@

The 3D surface area is calculated as following:
\begin{equation}
\label{eqn:eq7}
\text{3D surface area} = \sum \text{pixel area} \times \text{slope correction}
\end{equation}
